---
title: "13-GHA City Weather API"
author: Ramanathan Perumal
output:
  html_document:
    df_print: paged
---


```{r echo=FALSE}
now_asia <- function() {
   now <- Sys.time()
   attr(now, "tzone") <- "Asia/Calcutta"
   now
}
```
---
date: "Last compiled on `r now_asia()` , TZ: 'Asia/Calcutta'"
---


```{r setup, include=FALSE}

# date: "Last updated weather data on `r city_weather_now$datetime[1]`"

knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE, warning=FALSE}
library(dplyr)
library(pointblank)
library(openmeteo)
```

```{r echo=FALSE}
# load city geocode data
load("./data/city_gc.rda")
```

### Retrieve Current Weather from the Open-Meteo API

weather_now() calls the Open-Meteo weather API for the most recently recorded weather conditions a given location. We have used it for some of Indian cities.

```{r echo=FALSE}
# empty list
list_city_weather <- list()

# run through list object
for(i in 1:nrow(city_gc)){
  #print(city_gc$name[i])
  list_city_weather[[i]] <- weather_now(c(city_gc$latitude[i] , city_gc$longitude[i] ), timezone = city_gc$timezone[i])
}

city_weather_now <- do.call(rbind, list_city_weather) %>%
                    mutate(city = city_gc$name) %>%
                    relocate(city, .after = datetime ) %>%
                    dplyr::select(-weathercode)

city_weather_now



```

### Pointblank validation flow

```{r}
agent <- 
  create_agent(
    tbl = city_weather_now,
    tbl_name = "Weather Data",
    label = "Weather data from the Open-Meteo API"
  ) %>%
  col_is_posix(vars(datetime)) %>%
  col_vals_lt(vars(temperature), value = 32) %>%
  col_vals_between(vars(windspeed), left = 5, right = 10) %>%
  interrogate()
```

The full-featured display-table-based report can be viewed by printing the agent object;

```{r}
report <- get_agent_report(agent)
report
```
