---
title: "14-GHA Weather Pipe"
author: Ramanathan Perumal
output:
  html_document:
    theme: cosmo
    df_print: paged
---


```{r echo=FALSE}
now_asia <- function() {
   now <- Sys.time()
   attr(now, "tzone") <- "Asia/Calcutta"
   now
}
```
---
date: "Last compiled on `r now_asia()` , TZ: 'Asia/Calcutta'"
---


```{r setup, include=FALSE}

# date: "Last updated weather data on `r city_weather_now$datetime[1]`"

knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE, warning=FALSE}
library(pointblank)
library(openmeteo)
library(projmgr)
library(dplyr)
library(purrr)
library(glue)
library(knitr)
```

```{r echo=FALSE}
# load city geocode data
load("./data/city_gc.rda")
```

### Retrieve Current Weather from the Open-Meteo API

weather_now() calls the Open-Meteo weather API for the most recently recorded weather conditions a given location. We have used it for some of Indian cities.

```{r echo=FALSE}
# empty list
list_city_weather <- list()

# run through list object
for(i in 1:nrow(city_gc)){
  #print(city_gc$name[i])
  list_city_weather[[i]] <- weather_now(c(city_gc$latitude[i] , city_gc$longitude[i] ), timezone = city_gc$timezone[i])
}

city_weather_now <- do.call(rbind, list_city_weather) %>%
                    mutate(city = city_gc$name) %>%
                    relocate(city, .after = datetime ) %>%
                    dplyr::select(-weathercode)

```
```{r echo = FALSE}
avg_temp <- mean(city_weather_now$temperature) 
avg_temp <- round(avg_temp, 2)
```

```{r}
city_weather_now
```

Average temperature of the dataset is `r avg_temp` $^\circ$ C.



### Pointblank validation flow

```{r}
act <- action_levels(warn_at = 0.01, notify_at = 0.01, stop_at = NULL)
table_name <- "weather_data"

agent <- 
  create_agent(
    tbl = city_weather_now,
    tbl_name = "Weather Data",
    label = "Weather data from the Open-Meteo API",
    actions = act
  ) %>%
  col_is_posix(vars(datetime)) %>%
  col_vals_lte(vars(temperature), value = avg_temp) %>%
  col_vals_between(vars(windspeed), left = 5, right = 10)

res <- interrogate(agent)

```

The full-featured display-table-based report can be viewed by printing the agent object;

```{r}
report <- get_agent_report(res)
report
```


## Links to Open Issues

```{r post-to-github, echo =FALSE}
repo <- create_repo_ref("ramamet", "data_validation_automation", identifier = "GITHUB_PAT")

desc_components <- c(
  "Variables: {glue_collapse(column)}",
  "Date: {Sys.Date()}",
  "Frequency: {n_failed}/{n} ({f_failed})",
  "See full report at https://ramamet.github.io"
)
desc_template <- paste(desc_components, collapse = "\n")

out <- 
  res$validation_set %>%
  filter(warn) %>%
  select(columns_expr, brief, column, n, n_failed, f_failed) 

issues_df <-
  out %>%
  rowwise() %>%
  mutate(col_list = map(column, ~strsplit(., split = ", ")[[1]])) %>%
  transmute(
    title = glue("In {table_name}: {brief}"),
    body = glue(desc_template),
    label_table = glue("table:{table_name}"),
    label_vars  = list(glue("var:{col_list}"))
  ) %>%
  transmute(
    title,
    body,
    labels = list(c(label_table, unlist(label_vars)))
  )

issue_numbers <- purrr::pmap(issues_df, 
                      possibly(~post_issue(ref = repo, ...), otherwise = "")
                      )

```

```{r link-to-github, results = "asis", echo =FALSE}
issues_open <- 
  get_issues(repo, state = "open") %>%
  parse_issues() %>%
  arrange(number) %>%
  mutate(link = glue("[{number}. {title}]({url})"))

issues_open %>%
    rowwise() %>%
    select(
        `Open Since` = created_at,
        `Issue` = link,
        `Assigned` = assignees_login,
        `Activity` = n_comments
    ) %>%
  kable()
```